---
title: "hippohacks RMarkdown"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
## Introduction

In this hackathon we will be calling many different APi's in order to get information on different transportation stuffs. First goal is to get some of the venders.
```{r}
library(httr)
library(jsonlite)
library(broom)
library(dplyr)
```

```{r}
#define the function
get_Capital <- function(url) {
  doot <- fromJSON(url)
  doot2 <- doot$data
  doot3 <- do.call(what = "rbind",
                           args = lapply(doot2, as.data.frame))
  return(doot3)
}
```

```{r}
# Get capital bikeshare locations and status
station_DataDF <- get_Capital("https://gbfs.capitalbikeshare.com/gbfs/en/station_information.json")
station_statusDF <- get_Capital("https://gbfs.capitalbikeshare.com/gbfs/en/station_status.json")
station_BigData <- station_DataDF %>%
  left_join(station_statusDF, by = "station_id")
```

```{r}
library(DCmapR)
ward_df <- get_Ward(dataframe = TRUE)
ggplot() +
  geom_polygon(data = ward_df, aes(x = long, y = lat, group = group, fill = factor(Ward)),
               col  = "black", alpha = 0.3, size = 1) + 
  scale_fill_discrete(name = "Ward") + 
  geom_point(data = station_BigData, aes(x = lon, y = lat, group = station_id), col = "black") +
  coord_quickmap()
```

```{r}
library(plotly)
Sys.setenv('MAPBOX_TOKEN' = 'pk.eyJ1IjoibWFzdGVyYmluZ28xIiwiYSI6ImNqdDluOHo2aDAxenQ0OW51dmdkOGIyaDkifQ.KMv1Wkds1VtmtzOOmMWuiw')
plot_mapbox(mode = "scattermapbox", marker = list(symbol = "bicycle", size = 9.5, color = "blue")) %>%
  add_markers(data = station_BigData, x = ~ lon, y = ~ lat,
              hoverinfo = "text",
            text = ~paste('Name: ', name,
                          '\n Available Bikes: ', num_bikes_available,
                          '\n Available Docks: ', num_docks_available)) %>%
  layout(mapbox = list(zoom = 11,
                       center = list(lat = ~median(station_BigData$lat),
                                     lon = ~median(station_BigData$lon)),
                       style = "dark"))
#second version
plot_mapbox(mode = "scattermapbox", hoverlabel = list(
  bgcolor = "green", bordercolor = "white"
)) %>%
  add_markers(data = station_BigData, x = ~ lon, y = ~ lat, fill = "blue",
              hoverinfo = "text",
            text = ~paste('Name: ', name,
                          '\n Available Bikes: ', num_bikes_available,
                          '\n Available Docks: ', num_docks_available)) %>%
  layout(mapbox = list(zoom = 11,
                       center = list(lat = ~median(station_BigData$lat),
                                     lon = ~median(station_BigData$lon)),
                       style = "streets"))
```

## Goal 2

Lets try to find how to geocode addreses in R
First attempt will be with google maps

```{r}
library(ggmap)
homeLoc <- geocode("3230 7th st NE, washington dc", output = c("latlon"), source = "google")
destLoc <- geocode("1100 Pensylvania Ave NW, washington dc", output = c("latlon"), source = "google")
```

## Problem 3 

Find the closest bike closest:
```{r}
#grab some nifty stack overflow 
library(rgeos) 
set1sp <- SpatialPoints(homeLoc)
set2sp <- SpatialPoints(destLoc)
homeLoc$nearest_in_set2 <- apply(gDistance(set1sp, set2sp, byid=TRUE), 1, which.min)
station_sub <- station_BigData[, 6:5]
station_subSP <- SpatialPoints(station_sub)
blep <- gDistance(set1sp, station_subSP, byid=TRUE)
n <- station_BigData %>%
  cbind(blep)
n %>%
  arrange(`1`) %>%
  head(1L) %>%
  select(name, lat, lon)
```

Lets turn this into a usuable function for our backend server:
```{r define get_closests}
get_closest <- function(location){
  library(rgeos) #load packages
  location <- geocode(location, output = c("latlon"), source = "google")
  set1sp <- SpatialPoints(location) #define location points
  station_sub <- station_BigData[, 6:5]#subset for lon lat
  station_subSP <- SpatialPoints(station_sub)
  blep <- gDistance(set1sp)
  n <- station_BigData %>% #cbind back into larger data frame
    cbind(blep)
  dock <- n %>%
    arrange(`1`) %>%
    head(1L) %>%
    select(name, lat, lon)
  return(dock)
}
```
```{r}
location <-geocode("460 taylor st NE, washington dc", output = "latlon", source = "google")
 set1sp <- SpatialPoints(location) #define location points
 station_sub <- station_BigData[, 6:5]#subset for lon lat
 station_subSP <- SpatialPoints(station_sub)
 blep <- gDistance(set1sp)
```

